Pyro-Velocity

### 2024-03-25 nbs/tutorials/introduction.qmd
fix(nbs): update index Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>
fix(docs): sync description Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

>>>>

[Pyro-Velocity](https://docs.pyrovelocity.net) is a library for probabilistic inference in minimal models approximating gene expression dynamics from, possibly multimodal, single-cell sequencing data.
It provides posterior estimates of gene expression parameters, predictive estimates of gene expression states, and local estimates of cell state transition probabilities.
It can be used as a component in frameworks that attempt to retain the ability to propagate uncertainty in predicting: distributions over cell fates from subpopulations of cell states, response to cell state perturbations, or candidate genes or gene modules that correlate with determination of specific cell fates.
